Team size and composition in home health care

### 2023-10-26 paper-presentation/paper-presentation.qmd
Minor

::: r-fit-text
For some grade of service [$\gamma$]{style="color: red;"}, the required weekly capacity [$C$]{style="color: red;"} is $$C = \rho + \gamma z \rho$$

>>>>

::: r-fit-text
For some grade of service [$\gamma$]{style="color: red;"}, the required weekly capacity [$C$]{style="color: red;"} is $$C = \rho + \gamma \sqrt{z \rho}$$
